### 2022-08-23 hta/neurips_2022.tex
Updates from Overleaf

\documentclass{article}
\csname remappendix\endcsname

@@

% ready for submission
\usepackage{neurips_2022}

@@

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{array}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{hhline}
\usepackage{multirow}

\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\usepackage{todonotes}
\title{Static Analysis of Tail Behaviour with a \\ Generalized Gamma Algebra}

\newcommand{\feynman}[1]{\todo{(Feynman): #1}}
\newcommand{\dd}{\mathrm{d}}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{etoolbox}
\robustify\bfseries
\usepackage[ruled]{algorithm2e}
\usepackage{float}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

@@

\maketitle

\begin{abstract}
	Despite the successes of probabilistic models based on passing noise through
	neural networks, recent work has identified that such methods often fail to
	capture tail behavior accurately unless the tails of the base distribution
	are appropriately calibrated. To overcome this deficiency, we propose a
	systematic approach for analyzing the tails of random variables during the
	static analysis (before drawing samples) pass of a probabilistic programming
	language (PPL) compiler. To characterize how the tails change under
	algebraic operations, we develop an algebra acting on a three-parameter
	family of tail asymptotics based on the generalized Gamma distribution. Our
	algebraic operations are closed under addition and multiplication, capable
	of distinguishing sub-Gaussians with differing scales, and handle ratios
	sufficiently well to reproduce the tails of most important statistical
	distributions directly from their definitions. Our experiments confirm that
	inference algorithms leveraging generalized Gamma algebra metadata attain
	superior performance across a number of density modeling and variational
	inference tasks.
\end{abstract}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/schematic.pdf}
	\caption{Our overall approach for density approximations with calibrated tails.
		A generative model expressed in a PPL (1) and analyzed using the GGA (2) to
		compute the tail parameters of the target. A representative distribution
		with calibrated tails is chosen for the initial approximation (3) and a learnable
		Lipschitz pushforward (see \Cref{lem:lipschitz}) is optimized (4) to correct the
		bulk approximation.}
\end{figure}

@@

%% This declares a command \Comment
%% The argument will be surrounded by /* ... */
\SetKwComment{Comment}{/* }{ */}

\begin{algorithm}
	\caption{Pseudocode for a GGA tails static analysis pass}\label{alg:bfs_typecheck}
	\KwData{Abstract syntax tree for a PPL program}
	\KwResult{GGA parameter estimates for all random variables}
	frontier $\gets$ [rv : Parents(rv) = $\emptyset$]\;
	GGAs $\gets \{\}$\;
	\While{\text{frontier} $\neq \emptyset$}{
		next $\gets$ frontier.popLeft()\;
		GGAs[next] $\gets$ computeGGA(next.op, next.parent)\;
		frontier $\gets$ frontier + next.children()\;
	}
	\Return{GGAs}
\end{algorithm}

@@

	\begin{figure}[h]
		\centering
		\input{experiments/normal-power-sum.pgf}
		\input{experiments/lip-nf.pgf}
		\caption{(Top) $5000$ samples of $\lvert x^\top A y \rvert$ vs the
		calibrated GGA density $q(x)$. While calibrated tails are provably guarantees,
		the target distribution's bulk differs from the assumed generalized Gamma representative distribution (\cref{ssec:repr_dist}) for all $k$.
		To fix the bulk approximation, a normalizing flow is composed with
		the GGA representative to form $\text{flow}(q)(x)$. The bulk approximation
		is improved (bottom) while the tails continue to exhibit the same
		behavior (bottom right).
		}
		\label{fig:power_normal}
	\end{figure}

@@

\begin{ack}
	Use unnumbered first level headings for the acknowledgments. All acknowledgments
	go at the end of the paper before the list of references. Moreover, you are required to declare
	funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
	More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2021/PaperInformation/FundingDisclosure}.

	Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
\end{ack}

@@

{
\small
\bibliographystyle{unsrtnat}
\bibliography{refs}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Checklist}

@@

\begin{enumerate}

\item For all authors...
\begin{enumerate}
  \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \answerYes{}
  \item Did you describe the limitations of your work?
    \answerYes{See \cref{sec:conclusion}}
  \item Did you discuss any potential negative societal impacts of your work?
    \answerYes{See \cref{sec:conclusion}}
  \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
    \answerYes{}
\end{enumerate}

\item If you are including theoretical results...
\begin{enumerate}
  \item Did you state the full set of assumptions of all theoretical results?
    \answerYes{Stated at start of \cref{sec:gga}}
	\item Did you include complete proofs of all theoretical results?
    \answerYes{Most are deferred to supplementary materials}
\end{enumerate}

\item If you ran experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerYes{See supplemental, a URL for code will be provided witn camera ready}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerYes{}
	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerYes{Standard errors reported in parenthesis on \cref{tab:de} and \cref{tab:vi}}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerYes{See \cref{sec:experiments}}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerYes{See citations of \citep{tehrani2020bean}}
  \item Did you mention the license of the assets?
    \answerYes{Licence included in code}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerYes{See supplemental material}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerNA{}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerNA{}
\end{enumerate}

\item If you used crowdsourcing or conducted research with human subjects...
\begin{enumerate}
  \item Did you include the full text of instructions given to participants and screenshots, if applicable?
    \answerNA{}
  \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
    \answerNA{}
  \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
    \answerNA{}
\end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdefined\remappendix
\newpage

\appendix

@@

\fi
\end{document}

>>>>

\documentclass[thesis.tex]{subfiles}
% \documentclass{article}
\csname remappendix\endcsname

@@

% ready for submission
% \usepackage{neurips_2022}

@@

% \usepackage[utf8]{inputenc} % allow utf-8 input
% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
% \usepackage{hyperref}       % hyperlinks
% \usepackage{url}            % simple URL typesetting
% \usepackage{booktabs}       % professional-quality tables
% \usepackage{amsfonts}       % blackboard math symbols
% \usepackage{nicefrac}       % compact symbols for 1/2, etc.
% \usepackage{microtype}      % microtypography
% \usepackage{xcolor}         % colors
% \usepackage{longtable}
% \usepackage{wrapfig}
% \usepackage{array}
% \usepackage{enumerate}
% \usepackage{enumitem}
% \usepackage{hhline}
% \usepackage{multirow}

% \usepackage{amsmath}
% \usepackage{amsthm}
% \newtheorem{theorem}{Theorem}
% \newtheorem{proposition}{Proposition}
% \newtheorem{lemma}[theorem]{Lemma}
% \theoremstyle{definition}
% \newtheorem{definition}{Definition}
% \newtheorem{example}{Example}
% \usepackage{todonotes}
% \title{Static Analysis of Tail Behaviour with a \\ Generalized Gamma Algebra}

% \newcommand{\feynman}[1]{\todo{(Feynman): #1}}
% \newcommand{\dd}{\mathrm{d}}
% \usepackage{tikz}
% \usetikzlibrary{bayesnet}
% \usepackage{cleveref}
% \usepackage{listings}
% \usepackage{multirow}
% \usepackage{siunitx}
% \usepackage{etoolbox}
% \robustify\bfseries
% \usepackage[ruled]{algorithm2e}
% \usepackage{float}

% \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
% \newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

@@

% \maketitle

% \begin{abstract}
	Despite the successes of probabilistic models based on passing noise through
	neural networks, recent work has identified that such methods often fail to
	capture tail behavior accurately unless the tails of the base distribution
	are appropriately calibrated. To overcome this deficiency, we propose a
	systematic approach for analyzing the tails of random variables during the
	static analysis (before drawing samples) pass of a probabilistic programming
	language (PPL) compiler. To characterize how the tails change under
	algebraic operations, we develop an algebra acting on a three-parameter
	family of tail asymptotics based on the generalized Gamma distribution. Our
	algebraic operations are closed under addition and multiplication, capable
	of distinguishing sub-Gaussians with differing scales, and handle ratios
	sufficiently well to reproduce the tails of most important statistical
	distributions directly from their definitions. Our experiments confirm that
	inference algorithms leveraging generalized Gamma algebra metadata attain
	superior performance across a number of density modeling and variational
	inference tasks.
% \end{abstract}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{./figures/schematic.pdf}
	\caption{Our overall approach for density approximations with calibrated tails.
		A generative model expressed in a PPL (1) and analyzed using the GGA (2) to
		compute the tail parameters of the target. A representative distribution
		with calibrated tails is chosen for the initial approximation (3) and a learnable
		Lipschitz pushforward (see \Cref{lem:lipschitz}) is optimized (4) to correct the
		bulk approximation.}
\end{figure}

@@

%% This declares a command \Comment
%% The argument will be surrounded by /* ... */
% \SetKwComment{Comment}{/* }{ */}

\begin{algorithm}
	\caption{Pseudocode for a GGA tails static analysis pass}\label{alg:bfs_typecheck}
	\begin{algorithmic}
	\REQUIRE{Abstract syntax tree for a PPL program}

	\STATE{frontier $\gets$ [rv : Parents(rv) = $\emptyset$]}\\
	\STATE{GGAs $\gets \{\}$}

	\WHILE{\text{frontier} $\neq \emptyset$} 
	\STATE{next $\gets$ frontier.popLeft()}\\
	\STATE{GGAs[next] $\gets$ computeGGA(next.op, next.parent)}\\
	\STATE{frontier $\gets$ frontier + next.children()}
	\ENDWHILE

	\RETURN{GGA parameter estimates for all random variables}
	\end{algorithmic}
\end{algorithm}

@@

	\begin{figure}[h]
		\centering
		\input{./experiments/normal-power-sum.pgf}
		\input{./experiments/lip-nf.pgf}
		\caption{(Top) $5000$ samples of $\lvert x^\top A y \rvert$ vs the
		calibrated GGA density $q(x)$. While calibrated tails are provably guarantees,
		the target distribution's bulk differs from the assumed generalized Gamma representative distribution (\cref{ssec:repr_dist}) for all $k$.
		To fix the bulk approximation, a normalizing flow is composed with
		the GGA representative to form $\text{flow}(q)(x)$. The bulk approximation
		is improved (bottom) while the tails continue to exhibit the same
		behavior (bottom right).
		}
		\label{fig:power_normal}
	\end{figure}

@@

% \begin{ack}
% 	Use unnumbered first level headings for the acknowledgments. All acknowledgments
% 	go at the end of the paper before the list of references. Moreover, you are required to declare
% 	funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
% 	More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2021/PaperInformation/FundingDisclosure}.

% 	Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
% \end{ack}

@@

% {
% \small
% \bibliographystyle{unsrtnat}
% \bibliography{refs}
% }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Checklist}

@@

% \begin{enumerate}

% \item For all authors...
% \begin{enumerate}
%   \item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
%     \answerYes{}
%   \item Did you describe the limitations of your work?
%     \answerYes{See \cref{sec:conclusion}}
%   \item Did you discuss any potential negative societal impacts of your work?
%     \answerYes{See \cref{sec:conclusion}}
%   \item Have you read the ethics review guidelines and ensured that your paper conforms to them?
%     \answerYes{}
% \end{enumerate}

% \item If you are including theoretical results...
% \begin{enumerate}
%   \item Did you state the full set of assumptions of all theoretical results?
%     \answerYes{Stated at start of \cref{sec:gga}}
% 	\item Did you include complete proofs of all theoretical results?
%     \answerYes{Most are deferred to supplementary materials}
% \end{enumerate}

% \item If you ran experiments...
% \begin{enumerate}
%   \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
%     \answerYes{See supplemental, a URL for code will be provided witn camera ready}
%   \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
%     \answerYes{}
% 	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
%     \answerYes{Standard errors reported in parenthesis on \cref{tab:de} and \cref{tab:vi}}
% 	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
%     \answerYes{See \cref{sec:experiments}}
% \end{enumerate}

% \item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
% \begin{enumerate}
%   \item If your work uses existing assets, did you cite the creators?
%     \answerYes{See citations of \citep{tehrani2020bean}}
%   \item Did you mention the license of the assets?
%     \answerYes{Licence included in code}
%   \item Did you include any new assets either in the supplemental material or as a URL?
%     \answerYes{See supplemental material}
%   \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
%     \answerNA{}
%   \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
%     \answerNA{}
% \end{enumerate}

% \item If you used crowdsourcing or conducted research with human subjects...
% \begin{enumerate}
%   \item Did you include the full text of instructions given to participants and screenshots, if applicable?
%     \answerNA{}
%   \item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
%     \answerNA{}
%   \item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
%     \answerNA{}
% \end{enumerate}

% \end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \ifdefined\remappendix
% \newpage

% \appendix

@@

% \fi
\end{document}

### 2022-08-23 ic/aistats2021/paper.tex
Updates from Overleaf

\documentclass[twoside]{article}

%\usepackage{aistats2021}
\usepackage[accepted]{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

% If you set papersize explicitly, activate the following three lines:
\special{papersize = 8.5in, 11in}
\setlength{\pdfpageheight}{11in}
\setlength{\pdfpagewidth}{8.5in}

% If you use natbib package, activate the following three lines:
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

% If you use BibTeX in apalike style, activate the following line:
\bibliographystyle{apalike}

\input{macros.tex}

@@

\twocolumn[

  \aistatstitle{Accelerating Metropolis-Hastings with Lightweight Inference Compilation}

  \aistatsauthor{ Feynman Liang \And Nimar Arora \And Nazanin Tehrani \\ \\
    \AND Yucen Li \And Michael Tingley \And Erik Meijer }
  \vspace{-0.60in}
  \aistatsaddress{ UC Berkeley \\ feynman@berkeley.edu
    \And Facebook \\ nimarora@fb.com
    \And Facebook \\ nazaninkt@fb.com
    \AND Facebook \\ yucenli@fb.com
    \And Facebook \\ tingley@fb.com
    \And Facebook \\ erikm@fb.com}
]

\runningauthor{Liang, Arora, Tehrani, Li, Tingley, Meijer}
\begin{abstract}
  In order to construct accurate proposers for Metropolis-Hastings Markov
  Chain Monte Carlo, we integrate ideas from probabilistic graphical models
  and neural networks in a framework we call Lightweight
  Inference Compilation (LIC). LIC implements amortized inference within an
  open-universe declarative probabilistic programming language (PPL).
  Graph neural networks are used to parameterize proposal distributions
  as functions of Markov blankets, which during ``compilation'' are optimized
  to approximate single-site Gibbs sampling distributions. Unlike prior work
  in inference compilation (IC), LIC forgoes importance sampling of linear
  execution traces in favor of operating directly on Bayesian networks.
  Through using a declarative PPL, the Markov blankets of nodes (which may be
  non-static) are queried at inference-time to produce proposers. Experimental
  results show LIC can produce proposers which have less parameters, greater
  robustness to nuisance random variables, and improved posterior sampling in
  a Bayesian logistic regression and $n$-schools inference application.
\end{abstract}

@@

\bibliography{refs.bib}

>>>>

% \documentclass[twoside]{article}
\documentclass[thesis.tex]{subfiles}

%\usepackage{aistats2021}
% \usepackage[accepted]{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

% If you set papersize explicitly, activate the following three lines:
% \special{papersize = 8.5in, 11in}
% \setlength{\pdfpageheight}{11in}
% \setlength{\pdfpagewidth}{8.5in}

% If you use natbib package, activate the following three lines:
% \usepackage[round]{natbib}
% \renewcommand{\bibname}{References}
% \renewcommand{\bibsection}{\subsubsection*{\bibname}}

% If you use BibTeX in apalike style, activate the following line:
% \bibliographystyle{apalike}

% \input{macros.tex}

@@

% \twocolumn[

%   \aistatstitle{Accelerating Metropolis-Hastings with Lightweight Inference Compilation}

%   \aistatsauthor{ Feynman Liang \And Nimar Arora \And Nazanin Tehrani \\ \\
%     \AND Yucen Li \And Michael Tingley \And Erik Meijer }
%   \vspace{-0.60in}
%   \aistatsaddress{ UC Berkeley \\ feynman@berkeley.edu
%     \And Facebook \\ nimarora@fb.com
%     \And Facebook \\ nazaninkt@fb.com
%     \AND Facebook \\ yucenli@fb.com
%     \And Facebook \\ tingley@fb.com
%     \And Facebook \\ erikm@fb.com}
% ]

% \runningauthor{Liang, Arora, Tehrani, Li, Tingley, Meijer}
% \begin{abstract}
  In order to construct accurate proposers for Metropolis-Hastings Markov
  Chain Monte Carlo, we integrate ideas from probabilistic graphical models
  and neural networks in a framework we call Lightweight
  Inference Compilation (LIC). LIC implements amortized inference within an
  open-universe declarative probabilistic programming language (PPL).
  Graph neural networks are used to parameterize proposal distributions
  as functions of Markov blankets, which during ``compilation'' are optimized
  to approximate single-site Gibbs sampling distributions. Unlike prior work
  in inference compilation (IC), LIC forgoes importance sampling of linear
  execution traces in favor of operating directly on Bayesian networks.
  Through using a declarative PPL, the Markov blankets of nodes (which may be
  non-static) are queried at inference-time to produce proposers. Experimental
  results show LIC can produce proposers which have less parameters, greater
  robustness to nuisance random variables, and improved posterior sampling in
  a Bayesian logistic regression and $n$-schools inference application.
% \end{abstract}

@@

% \bibliography{refs.bib}
